manuscript_figures

### 2024-07-16 scripts/manuscript_figures.Rmd
annotated production values

# Now you can use this new 'Species' column in your ggplot
production_plot <- ggplot(pb_summary, aes(x = YEAR, y = mean_production, color = TREATMENT, group = TREATMENT)) +
  geom_point(size = 2) +         # Add points
  geom_line() +          # Add lines
  geom_errorbar(aes(ymin = mean_production - se_production, ymax = mean_production + se_production), width = 0.2) +  # Add error bars
  labs(x = "Year",  # X-axis label
       y = expression("Fish Production" ~ (g ~ m^-2 ~ yr^-1)),  # Y-axis label
       color = "Habitat") +  # Legend title
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 18),  # Rotate x-axis labels if needed
        axis.title.x = element_text(vjust = -0.5, size = 18),  # Adjust x-axis title position
        axis.title.y = element_text(vjust = 1.5, size = 18),
        axis.text.y = element_text(size = 18),
        legend.text = element_text(size = 16),
        legend.title = element_text(size = 18)) +
  scale_y_continuous(limits = c(0, 8), expand = c(0, 0));production_plot # Additional attempt to change legend title  # Use viridis colorblind-friendly palette

@@

# Step 4: Plot the data
production_diff_plot <- ggplot(merged_data, aes(x = YEAR, y = production_difference, group = TREATMENT_kelp)) +
  geom_point(size = 2) +  # Points with light blue outline
  geom_line() +  # Lines with light blue color
  geom_errorbar(aes(ymin = production_difference - se_difference, ymax = production_difference + se_difference), 
                width = 0.2, color = "black", size = 0.7) +  # Error bars
  labs(x = "Year",  # X-axis label
       y = expression("Kelp Habitat Fish Production" ~ (g ~ m^-2 ~ yr^-1)),  # Y-axis label
       color = "Treatment") +  # Legend title
  theme_bw() +  # White background with black lines
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 18),  # Rotate x-axis labels if needed
        axis.title.x = element_text(vjust = -0.5, size = 18),  # Adjust x-axis title position
        axis.title.y = element_text(vjust = 1.5, size = 18),  # Adjust y-axis title position
        axis.text.y = element_text(size = 18),  # Adjust y-axis text size
        legend.text = element_text(size = 16),  # Legend text size
        legend.title = element_text(size = 18));production_diff_plot

@@

>>>>

# Now you can use this new 'Species' column in your ggplot
production_plot <- ggplot(pb_summary, aes(x = YEAR, y = mean_production, color = TREATMENT, group = TREATMENT)) +
  geom_point(size = 3) +         # Add points
  geom_line() +          # Add lines
  geom_errorbar(aes(ymin = mean_production - se_production, ymax = mean_production + se_production), width = 0.2) +  # Add error bars
  labs(x = "Year",  # X-axis label
       y = expression("Fish Production" ~ (g ~ m^-2 ~ yr^-1)),  # Y-axis label
       color = "Habitat") +  # Legend title
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 18),  # Rotate x-axis labels if needed
        axis.title.x = element_text(vjust = -0.5, size = 18),  # Adjust x-axis title position
        axis.title.y = element_text(vjust = 1.5, size = 18),
        axis.text.y = element_text(size = 18),
        legend.text = element_text(size = 16),
        legend.title = element_text(size = 18)) +
  scale_y_continuous(limits = c(0, 8), expand = c(0, 0));production_plot # Additional attempt to change legend title 
#blue color is #00BFC4

@@

# Step 4: Plot the data
production_diff_plot <- ggplot(merged_data, aes(x = YEAR, y = production_difference, group = TREATMENT_kelp)) +
  geom_point(size = 3) +  # Points in skyblue color
  geom_line() +  # Lines in skyblue color
  geom_errorbar(aes(ymin = production_difference - se_difference, ymax = production_difference + se_difference), 
                width = 0.2, color = "black", size = 0.7) +  # Error bars
  labs(x = "Year",  # X-axis label
       y = expression("Kelp Habitat Fish Production" ~ (g ~ m^-2 ~ yr^-1)),  # Y-axis label
       color = "Treatment") +  # Legend title
  theme_bw() +  # White background with black lines
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 18),  # Rotate x-axis labels if needed
        axis.title.x = element_text(vjust = -0.5, size = 18),  # Adjust x-axis title position
        axis.title.y = element_text(vjust = 1.5, size = 18),  # Adjust y-axis title position
        axis.text.y = element_text(size = 18),  # Adjust y-axis text size
        legend.text = element_text(size = 16),  # Legend text size
        legend.title = element_text(size = 18));production_diff_plot

# Update production_diff_plot with annotations
production_diff_plot_annot <- production_diff_plot +
  geom_text(aes(label = sprintf("%.2f", production_difference), y = production_difference),
            color = "black", size = 4, vjust = 2.42, hjust = 1.06, check_overlap = TRUE);production_diff_plot_annot

@@

# Save the combined plot
ggsave("output/figures/fish_production.png", prod_combined_plot, width = 12, height = 8, units = "in", dpi = 300)
